A unified pseudo-$C_\ell$ framework

### 2018-08-30 doc/Paper/main.tex
modified figs 2 and 5 according to ref. report

      \subsubsection{Galaxy clustering and weak lensing} \label{sssec:validation.suite.lss}
        \begin{figure}
          \centering
          \includegraphics[width=0.99\columnwidth]{cls_lss}
          \caption{Signal and noise power spectra used in the LSS validation set. Red, green and blue curves show the spectra associated with the $\delta$-$\delta$, $\delta$-$\gamma_E$ and $\gamma_E$-$\gamma_E$ correlations respectively, where $\gamma_E$ is the lensing $E$ mode. All other cross-correlations are zero. The dashed lines show the noise power spectra, associated with shot noise (red) and intrinsic shape scatter (blue).} \label{fig:lss_cls}
        \end{figure}
        \begin{figure*}
          \centering
          \includegraphics[width=0.9\textwidth]{maps_lss_sph}
          \caption{Inputs for the large-scale structure, curved-sky validation set. From top to bottom and left to right: sky mask (1), Gaussian realization of the galaxy overdensity $\delta$ (2) and cosmic shear $\gamma_i$ (3,4), dust contaminant for $\delta$ (5), star contaminant for $\delta$ (6), PSF contaminant for $\gamma$ (7, $Q$ component) and small-scale contaminant for $\gamma$ (8, $Q$ component).}
          \label{fig:lss_mocks_sph}
        \end{figure*}
        \begin{figure*}
          \centering
          \includegraphics[width=0.9\textwidth]{maps_lss_flat}
          \caption{Same as Fig. \ref{fig:lss_mocks_sph} for the large-scale structure, flat-sky validation set.}
          \label{fig:lss_mocks_flat}
        \end{figure*}
        \begin{figure}
          \centering
          \includegraphics[width=0.99\columnwidth]{cls_cont_lss}
          \caption{{\sl Top:} signal power spectrum (red) for the auto-correlation of the galaxy overdensity, as well as the contaminants associated to dust (green) and stars (blue). {\sl Middle:} $E$-mode lensing power spectrum (red) and the spectra of the PSF and small-scale contaminants used in our validation set (green and blue respectively). {\sl Bottom:} same as middle panel for the $B$-mode power spectrum. Note that in this case the input signal power spectrum is $0$. In all cases the yellow line shows the combination of signal and contaminants.} \label{fig:lss_cont_cls}
        \end{figure}
        The first validation suite exemplifies the use of pseudo-$C_\ell$ algorithms in the analysis of large-scale structure data. Current and next-generation imaging surveys such as DES~\citep{2016MNRAS.460.1270D},
        KiDS~\citep{2017A&A...604A.134D}, HSC~\citep{2018PASJ...70S...4A}, LSST~\citep{2008arXiv0805.2366I} and Euclid~\citep{2011arXiv1110.3193L} will constrain the growth and geometry of structure through cosmic time by using the overdensity of galaxies as a proxy for the matter inhomogeneities (a spin-0 field) and their correlated shape distortions (a spin-2 field at first order), mostly caused by weak lensing. These measurements will mostly follow a tomographic approach, using the angular auto- and cross-power spectra between these observables across different bins of photometric redshift \citep{2017arXiv170609359K,2018MNRAS.474.4894J,2017arXiv170801530D}.

>>>>

      \subsubsection{Galaxy clustering and weak lensing} \label{sssec:validation.suite.lss}
        \begin{figure}
          \centering
          \includegraphics[width=0.99\columnwidth]{cls_lss}
          \caption{Signal and noise power spectra used in the LSS validation set. Dark blue, cyan and red curves show the spectra associated with the $\delta$-$\delta$, $\delta$-$\gamma_E$ and $\gamma_E$-$\gamma_E$ correlations respectively, where $\gamma_E$ is the lensing $E$ mode. All other cross-correlations are zero. The dashed lines show the noise power spectra, associated with shot noise (red) and intrinsic shape scatter (blue).} \label{fig:lss_cls}
        \end{figure}
        \begin{figure*}
          \centering
          \includegraphics[width=0.9\textwidth]{maps_lss_sph}
          \caption{Inputs for the large-scale structure, curved-sky validation set. From top to bottom and left to right: sky mask (1), Gaussian realization of the galaxy overdensity $\delta$ (2) and cosmic shear $\gamma_i$ (3,4), dust contaminant for $\delta$ (5), star contaminant for $\delta$ (6), PSF contaminant for $\gamma$ (7, $Q$ component) and small-scale contaminant for $\gamma$ (8, $Q$ component).}
          \label{fig:lss_mocks_sph}
        \end{figure*}
        \begin{figure*}
          \centering
          \includegraphics[width=0.9\textwidth]{maps_lss_flat}
          \caption{Same as Fig. \ref{fig:lss_mocks_sph} for the large-scale structure, flat-sky validation set.}
          \label{fig:lss_mocks_flat}
        \end{figure*}
        \begin{figure}
          \centering
          \includegraphics[width=0.99\columnwidth]{cls_cont_lss}
          \caption{{\sl Top:} signal power spectrum (solid dark blue) for the auto-correlation of the galaxy overdensity, as well as the contaminants associated to dust (dashed cyan) and stars (dot-dashed red). {\sl Middle:} $E$-mode lensing power spectrum (solid dark blue) and the spectra of the PSF and small-scale contaminants used in our validation set (dashed cyan and dot-dashed red respectively). {\sl Bottom:} same as middle panel for the $B$-mode power spectrum. Note that in this case the input signal power spectrum is $0$. In all cases the orange dotted line shows the combination of signal and contaminants.} \label{fig:lss_cont_cls}
        \end{figure}
        The first validation suite exemplifies the use of pseudo-$C_\ell$ algorithms in the analysis of large-scale structure data. Current and next-generation imaging surveys such as DES~\citep{2016MNRAS.460.1270D},
        KiDS~\citep{2017A&A...604A.134D}, HSC~\citep{2018PASJ...70S...4A}, LSST~\citep{2008arXiv0805.2366I} and Euclid~\citep{2011arXiv1110.3193L} will constrain the growth and geometry of structure through cosmic time by using the overdensity of galaxies as a proxy for the matter inhomogeneities (a spin-0 field) and their correlated shape distortions (a spin-2 field at first order), mostly caused by weak lensing. These measurements will mostly follow a tomographic approach, using the angular auto- and cross-power spectra between these observables across different bins of photometric redshift \citep{2017arXiv170609359K,2018MNRAS.474.4894J,2017arXiv170801530D}.
